Analysis

### 2020-02-25 reports/DRM_exp/analysis_DRM_exp1.Rmd
few more tests

cor.test(~dist_to_proto+correct, df2)

>>>>

cor.test(~dist_to_proto+correct, df2)
cor.test(~dist_to_proto+correct, df2 %>% filter(type == "far distractor"))
cor.test(~dist_to_proto+correct, df2 %>% filter(type == "close distractor"))
cor.test(~dist_to_proto+correct, df2 %>% filter(type == "target"))

df2 %>% 
  group_by(subject_id, type) %>% 
  summarize(correct = mean(correct),
            dist_to_proto = mean(dist_to_proto)) %>% 
  ggplot(aes(x=dist_to_proto,y=correct, col = type)) + 
  geom_point()
```
